Bayesian non-parametric inference for multivariate peaks-over-threshold models

### 2023-07-07 methodology_projgamma.tex
blah
prep for submission

\subsection{Projected gamma family\label{subsec:projgamma}}
To obtain a distribution on 
${\mathbb S}_{p}^{d-1}=\{\bm{s} : \bm{s} \in {\mathbb R}_{+}^{d}, \| \bm{s}\|_{p} = 1\}$ 
we start with a vector in 
$\bm{x} \in {\mathbb R}^d_+$, calculate its $\mathcal{L}_p$-norm  defined as
  \begin{equation*}
    \lVert \bm{x} \rVert_p = 
    \left({\textstyle\sum}_{\ell = 1}^d \lvert s_{\ell}\rvert^p\right)^{\frac{1}{p}},
  \end{equation*}
  and normalize it to obtain $\bm{y} = \bm{x}/\|\bm{x}\|_p \in {\mathbb S}_p^{d-1}$. 
  The absolute and Euclidean norms are obtained for $p=1$ and $p=2$ respectively,
  and the $\mathcal{L}_{\infty}$ norm can be obtained as a limit, 
  \begin{equation*}
    \| \bm{s} \|_{\infty}
      = \lim\limits_{p\to\infty} \| \bm{s} \|
      = \underset{\ell = 1}{\overset{d}{\bigvee}}s_{\ell}.
  \end{equation*}

A natural  distribution to consider in ${\mathbb R}^d_+$ is given by a product of independent
  univariate Gamma distributions. Let
    $\bm{ X} \sim \prod_{\ell = 1}^d\text{Ga}\left(X_{\ell}\mid\alpha_{\ell},\beta_{\ell}\right)$, 
    $\alpha_\ell$ and $\beta_\ell$ are the shape and scale parameters, respectively. 
    For any finite $p$, letting 
   $ y_d = (1 - {\textstyle\sum}_{\ell = 1}^{d-1}y_{\ell}^p)^{1/p}$,
    the transformation
  \begin{equation}
    \label{eqn:pnormt}
    \begin{aligned}
    T(x_1,\ldots,x_d) &= \left(\pnorm{\bm{x}}{p}, \frac{x_1}{\pnorm{\bm{x}}{p}},
                          \ldots , \frac{x_{d-1}}{\pnorm{\bm{x}}{p}}\right) \\
                        &= (r,y_1,\ldots,y_{d-1})
    \end{aligned}
  \end{equation}
  is invertible with
  \begin{equation}
    \label{eqn:pnormtinv}
    \begin{aligned}
    &\hspace{-0.5cm}T^{-1}\left(r,y_1,\ldots,y_{d-1}\right)\\
      & = \left(ry_1,\ldots,ry_{d-1}, 
        r\left(1 - {\textstyle\sum}_{\ell = 1}^{d-1}y_{\ell}^p\right)^{\frac{1}{p}}\right).
    \end{aligned}
  \end{equation}
  The Jacobian of the transformation takes the form
  \begin{equation}
    \label{eqn:pnormjac}
    \begin{aligned}
    r^{d-1}\left[\left(1 - {\textstyle\sum}_{\ell = 1}^{d-1}y_{\ell}^p\right)^{\frac{1}{p}} \right. & \\
        &\hspace{-2cm}+ \left. {\textstyle\sum}_{\ell = 1}^{d-1}y_{\ell}^p
          \left(1 - {\textstyle\sum}_{l=1}^{d-1} y_{\ell}^p\right)^{\frac{1}{p} - 1}\right].
    \end{aligned}
  \end{equation}
  The normalization provided by $T$ maps a vector in ${\mathbb R}_+^d$ onto
  ${\mathbb S}_p^{d-1} $. With a slight abuse of terminology we refer to it as a
  projection. Using Equations (\ref{eqn:pnormt}) -- (\ref{eqn:pnormjac}) we have the joint density
  \begin{equation}
  \label{joint}
    \begin{aligned}
    f(r,\bm{ y}) = &\prod_{\ell = 1}^{d}
      \left[\frac{\beta_{\ell}^{\alpha_{\ell}}}{\Gamma(\alpha_{\ell})}(ry_{\ell})^{\alpha_{\ell} - 1}
          \exp\lbrace-\beta_{\ell}ry_{\ell}\rbrace\right] \\
      &\hspace{0.5cm}\times r^{d-1}\left[y_d +
            {\textstyle \sum}_{\ell = 1}^{d-1}y_{\ell}^p\left(y_d^p\right)^{\frac{1}{p} - 1}\right].
    \end{aligned}
  \end{equation}
  Integrating out $r$ yields the resulting \emph{Projected Gamma} density
  \begin{equation}
    \label{eqn:projgamma}
    \begin{aligned}
    \text{PG}(\bm{ y}\mid\bm{ \alpha},\bm{ \beta}) &=
          \prod_{\ell = 1}^d\left[\frac{\beta_{\ell}^{\alpha_{\ell}}}{\Gamma(\alpha_{\ell})}
                y_{\ell}^{\alpha_{\ell} - 1}\right]\\
      &\hspace{0.5cm}\times \left[y_d +
          {\textstyle \sum}_{\ell = 1}^{d-1}y_{\ell}^p\left(y_d^p\right)^{\frac{1}{p} - 1}\right]\\
      &\hspace{0.5cm}\times \frac{\Gamma({\textstyle\sum}_{\ell = 1}^d\alpha_{\ell})}{\left({\textstyle\sum}_{\ell = 1}^d
                    \beta_{\ell}y_{\ell}\right)^{{\scriptstyle\sum_{\ell = 1}^d \alpha_{\ell}}}},
    \end{aligned}
  \end{equation}
  defined for $\bm{y}\in {\mathbb S}_p^{d-1}$, and for any finite $p>0$. To avoid identifiability 
  problems when estimating the shape and scale parameters, we set $\beta_1 = 1$.
  \cite{nunez2019} obtain the density in Equation (\ref{eqn:projgamma})
  for $p=2$ as a multivariate distribution for directional data, using spherical coordinates.  
  For $\bm{ y}\in {\mathbb S}_1^{d-1}$, and $\beta_{\ell} = \beta$ for all $\ell$, the density in Equation (\ref{eqn:projgamma}) corresponds to that of a Dirichlet distribution.

@@

\subsubsection{Inference for the projected Gamma mixture model}
In a sample-based inference approach, for a given iteration the Dirichlet process mixture model 
    groups observations into stochastically assigned clusters, where members of a cluster share 
    distributional parameters \citep{ascolani2022}. Building out the methods of inference for Equation~(\ref{eqn:dppg}), 
    let $n_j^{-i}$ be the number of observations in cluster $j$ not including observation $i$.  Let $J^{-i}$ be 
    the number of extant clusters, not including any singleton that observation $i$ is in. Under this model, 
    the probability of cluster membership for a given observation is proportional to
\begin{equation*}
    \text{Pr}\left[\delta_i = j\mid\ldots\right] \propto \begin{cases}
        n_j^{-i}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\\ % \hspace{0.5cm} \\ % &\text{~for~}j \in \lbrace 1,\ldots,J^{-i}\rbrace\\
        \eta\int\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)dG_0(\bm{\alpha}_j,\bm{\beta}_j),%\hspace{0.5cm} % &\text{~for~}j = J^{-i} + 1.
        \end{cases}
\end{equation*}
where the top case is iterating over extant clusters $j = 1,\ldots, J^{-i}$, and the bottom case is
    for a \emph{new} cluster. If $G_0$ is not a conjugate prior for the kernel density, the integral in the 
    above formula may not be available in closed form. We sidestep this using Algorithm 8 from \cite{neal2000}: 
    by Monte Carlo integration, we draw $m$ candidate clusters, $\bm{\alpha}_j,\bm{\beta}_j$ for
    $j = J^{-i} + 1,\ldots, J^{-i} + m$ from $G_0$. Then, we sample the cluster indicator 
    $\gamma_i$ from extant or candidate clusters, where the probability of cluster membership is proportional to
\begin{equation}
    \text{Pr}\left[\delta_i = j\mid\ldots\right] \propto \begin{cases}
        n_j^{-i}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\\ % \hspace{0.5cm}  % &\text{~for~}j \in \lbrace 1,\ldots,J^{-i}\rbrace\\
        \frac{\eta}{m}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right). % \hspace{0.5cm} &\text{~for~}j \in \lbrace J^{-i} + 1,\ldots, J^{-i} + m\rbrace.
        \end{cases}
\end{equation}
Again, the top case is iterating over extant clusters, and now the bottom case is iterating 
    over new \emph{candidate} clusters.  If a candidate cluster is selected,
%{\bf you first have to say that you sample from this distribution. What is the ``candidate cluster''?}
    then $\gamma_i = J = J^{- i} + 1$, and the associated cluster parameters are saved.

@@

This model is completed with independent Gamma priors on $\xi_{\ell}$, $\tau_{\ell}$, $\zeta_{\ell}$, $\sigma_{\ell}$.  We also assume a Gamma prior on $\eta$, that is updated via the procedure outlined in \cite{escobar1995}.  We refer to this model as the \emph{projected Gamma--Gamma} (PG--G) model.  An advantage of the PG--G model is that, thanks to conjugacy, the rate parameters can easily be integrated out for inference on $\bm{\alpha}_j$.  Then, the full conditional for $\alpha_{j\ell}$ takes the form

@@

for $\ell = 2,\ldots, d$.  Updating $\beta_{j\ell}$ is done via a Gibbs step.  The hyper-parameters $\xi_{\ell},\tau_{\ell},\zeta_{\ell},\sigma_{\ell}$ follow similar Gamma-Gamma update relationships.  We also explore a restricted form of this model, where $\beta_{\ell} = 1$ for all $\ell$.  Under this model, we use the full conditional in Equation~(\ref{eqn:alpha1update}) for all $\ell$, and omit inference on $\bm{\zeta},\bm{\sigma}$.  We refer to this model as the \emph{projected restricted Gamma--Gamma} (PRG--G) model.

The second form of centering distribution we explore is a multivariate log-normal distribution on the shape parameters $\bm{\alpha}_j$, with independent Gamma $\beta_{j\ell}$ rate parameters.  
    \begin{equation}
        \begin{aligned}
        &\hspace{-0.5cm}G_0\left(\bm{\alpha}_j,\bm{\beta}_j\mid\bm{\mu},\bm{\Sigma},\zeta,\sigma\right) \\
        &=\mathcal{LN}\left(\bm{\alpha}_j\mid\bm{\mu},\bm{\Sigma}\right)\times\prod_{\ell = 2}^d\mathcal{G}\left(\beta_{j\ell}\mid\zeta_{\ell},\sigma_{\ell}\right).
        \end{aligned}
    \end{equation}
    This model is completed with a normal prior on $\bm{\mu}$, an inverse Wishart prior on
    $\bm{\Sigma}$, and Gamma priors on $\zeta_{\ell}$ and $\sigma_{\ell}$, and $\eta$.  
    This model is denoted as the \emph{projected Gamma--log-normal} (PG--LN) model.  
    We also explore a restricted Gamma form of this model as above, where 
    $\beta_{\ell} = 1$ for all $\ell$.  This is denoted as the 
    \emph{projected restricted gamma--log-normal} (PRG--LN) model.  Updates for 
    $\bm{\alpha}$ can be accomplished using a joint Metropolis step, where 
    $\beta_{j\ell}$ for $\ell = 2,\ldots,d$ have been integrated out of the 
    log-density.  That is,
    \begin{equation*}
        \begin{aligned}
        &\hspace{-0.5cm}\pi(\bm{\alpha}_j\mid\bm{Y},\bm{r},\bm{\delta},\bm{\mu},\bm{\Sigma},\bm{\zeta},\bm{\sigma})\\
        &\propto \exp\left\lbrace-\frac{1}{2}(\log\bm{\alpha}_j - \mu)^T\bm{\Sigma}^{-1}(\log\bm{\alpha}_j - \mu)\right\rbrace \\
        &\hspace{0.5cm}\times\frac{1}{\prod_{\ell = 1}^d\alpha_{j\ell}}\times \frac{\left(\prod_{i:\gamma_i = j}r_iy_{i1}\right)^{\alpha_{j1} - 1}}{\prod_{\ell = 1}^d\Gamma^{n_j}(\alpha_{j\ell})}\\
        &\hspace{0.5cm}\times \prod_{\ell = 2}^d\frac{\Gamma\left(n_j\alpha_{j\ell} + \zeta_{\ell}\right)}{\left(\sum_{i:\gamma_i = j}r_iy_{i\ell} + \sigma_{\ell}\right)^{n_j\alpha_{j\ell} + \zeta_{\ell}}}
        \end{aligned}
    \end{equation*}
    The inferential forms for $\beta_{j\ell}$ and its priors are the same as for PG--G.  The 
  normal prior for $\mu$ is conjugate for the log-normal $\bm{\alpha}_j$, and can be sampled
  via a Gibbs step.  Finally, the inverse Wishart prior for $\Sigma$ is again conjugate to
  the log-normal $\bm{\alpha}_j$, implying that it can also be sampled via a Gibbs step.

>>>>

\subsection{Projected gamma family\label{subsec:projgamma}}
The $\mathcal{L}_p$-norm, for $p>0$ is  defined as
  \begin{equation*}
    \lVert \bm{x} \rVert_p = 
    \left({\textstyle\sum}_{\ell = 1}^d \lvert s_{\ell}\rvert^p\right)^{\frac{1}{p}},
  \end{equation*}
The absolute and Euclidean norms are obtained for $p=1$ and $p=2$ respectively,
  and the $\mathcal{L}_{\infty}$ norm can be obtained as a limit, 
  \begin{equation*}
    \| \bm{s} \|_{\infty}
      = \lim\limits_{p\to\infty} \| \bm{s} \|
      = \underset{\ell = 1}{\overset{d}{\bigvee}}s_{\ell}.
  \end{equation*}

To obtain a distribution on 
${\mathbb S}_{p}^{d-1}=\{\bm{s} : \bm{s} \in {\mathbb R}_{+}^{d}, \| \bm{s}\|_{p} = 1\}$ 
we start with a vector in 
$\bm{x} \in {\mathbb R}^d_+$, and normalize it to obtain 
$\bm{y} = \bm{x}/\|\bm{x}\|_p \in {\mathbb S}_p^{d-1}$. 
A natural  distribution to consider in ${\mathbb R}^d_+$ is given by a product of independent
  univariate Gamma distributions. Let
    $\bm{ X} \sim \prod_{\ell = 1}^d\text{Ga}\left(X_{\ell}\mid\alpha_{\ell},\beta_{\ell}\right)$, 
    $\alpha_\ell$ and $\beta_\ell$ are the shape and scale parameters, respectively. 
    For any finite $p>0$, letting 
   $ y_d = (1 - {\textstyle\sum}_{\ell = 1}^{d-1}y_{\ell}^p)^{1/p}$,
    the transformation
  \begin{equation}
    \label{eqn:pnormt}
    \begin{aligned}
    T(x_1,\ldots,x_d) &= \left(\pnorm{\bm{x}}{p}, \frac{x_1}{\pnorm{\bm{x}}{p}},
                          \ldots , \frac{x_{d-1}}{\pnorm{\bm{x}}{p}}\right) \\
                        &= (r,y_1,\ldots,y_{d-1})
    \end{aligned}
  \end{equation}
  is invertible with
  \begin{equation}
    \label{eqn:pnormtinv}
    \begin{aligned}
    &\hspace{-0.5cm}T^{-1}\left(r,y_1,\ldots,y_{d-1}\right)\\
      & = \left(ry_1,\ldots,ry_{d-1}, 
        r\left(1 - {\textstyle\sum}_{\ell = 1}^{d-1}y_{\ell}^p\right)^{\frac{1}{p}}\right).
    \end{aligned}
  \end{equation}
  The Jacobian of the transformation takes the form
  \begin{equation}
    \label{eqn:pnormjac}
    \begin{aligned}
    r^{d-1}\left[\left(1 - {\textstyle\sum}_{\ell = 1}^{d-1}y_{\ell}^p\right)^{\frac{1}{p}} \right. & \\
        &\hspace{-2cm}+ \left. {\textstyle\sum}_{\ell = 1}^{d-1}y_{\ell}^p
          \left(1 - {\textstyle\sum}_{l=1}^{d-1} y_{\ell}^p\right)^{\frac{1}{p} - 1}\right].
    \end{aligned}
  \end{equation}
  The normalization provided by $T$ maps a vector in ${\mathbb R}_+^d$ onto
  ${\mathbb S}_p^{d-1} $. With a slight abuse of terminology we refer to it as a
  projection. Using Equations (\ref{eqn:pnormt}) -- (\ref{eqn:pnormjac}) we have the joint density
  \begin{equation}
  \label{joint}
    \begin{aligned}
    f(r,\bm{ y}) = &\prod_{\ell = 1}^{d}
      \left[\frac{\beta_{\ell}^{\alpha_{\ell}}}{\Gamma(\alpha_{\ell})}(ry_{\ell})^{\alpha_{\ell} - 1}
          \exp\lbrace-\beta_{\ell}ry_{\ell}\rbrace\right] \\
      &\hspace{0.5cm}\times r^{d-1}\left[y_d +
            {\textstyle \sum}_{\ell = 1}^{d-1}y_{\ell}^p y_d^{1 - p}\right].
    \end{aligned}
  \end{equation}
  Integrating out $r$ yields the resulting \emph{Projected Gamma} density
  \begin{equation}
    \label{eqn:projgamma}
    \begin{aligned}
    \text{PG}(\bm{ y}\mid\bm{ \alpha},\bm{ \beta}) &=
          \prod_{\ell = 1}^d\left[\frac{\beta_{\ell}^{\alpha_{\ell}}}{\Gamma(\alpha_{\ell})}
                y_{\ell}^{\alpha_{\ell} - 1}\right]\\
      &\hspace{0.5cm}\times \left[y_d +
          {\textstyle \sum}_{\ell = 1}^{d-1}y_{\ell}^p y_d^{1 - p}\right]\\
      &\hspace{0.5cm}\times \frac{\Gamma({\textstyle\sum}_{\ell = 1}^d\alpha_{\ell})}{\left({\textstyle\sum}_{\ell = 1}^d
                    \beta_{\ell}y_{\ell}\right)^{{\scriptstyle\sum_{\ell = 1}^d \alpha_{\ell}}}},
    \end{aligned}
  \end{equation}
  defined for $\bm{y}\in {\mathbb S}_p^{d-1}$, and for any finite $p>0$. To avoid identifiability 
  problems when estimating the shape and scale parameters, we set $\beta_1 = 1$.
  \cite{nunez2019} obtain the density in Equation (\ref{eqn:projgamma})
  for $p=2$ as a multivariate distribution for directional data, using spherical coordinates.  
  For $\bm{ y}\in {\mathbb S}_1^{d-1}$, and $\beta_{\ell} = \beta$ for all $\ell$, the density in
  Equation (\ref{eqn:projgamma}) corresponds to that of a Dirichlet distribution.

@@

\subsubsection{Inference for the projected Gamma mixture model}
In a sample-based inference approach, for a given iteration the Dirichlet process mixture model 
    groups observations into stochastically assigned clusters, where members of a cluster share 
    distributional parameters \citep{muller2015,ascolani2022}. Building out the methods of inference for Equation~(\ref{eqn:dppg}), 
    let $n_j^{-i}$ be the number of observations in cluster $j$ not including observation $i$.  Let $J^{-i}$ be 
    the number of extant clusters, not including any singleton containing observation $i$. Under this model, 
    the probability of cluster membership for a given observation is proportional to
\begin{equation*}
    \text{Pr}\left[\delta_i = j\mid\ldots\right] \propto \begin{cases}
        n_j^{-i}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\\ % \hspace{0.5cm} \\ % &\text{~for~}j \in \lbrace 1,\ldots,J^{-i}\rbrace\\
        \eta\int\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)dG_0(\bm{\alpha}_j,\bm{\beta}_j),%\hspace{0.5cm} % &\text{~for~}j = J^{-i} + 1.
        \end{cases}
\end{equation*}
where the top case is iterating over extant clusters $j = 1,\ldots, J^{-i}$, and the bottom case is
    for a \emph{new} cluster. If $G_0$ is not a conjugate prior for the kernel density, the integral in the 
    above formula may not be available in closed form. We sidestep this using Algorithm 8 from \cite{neal2000}: 
    by Monte Carlo integration, we draw $m$ candidate clusters, $\bm{\alpha}_j,\bm{\beta}_j$ for
    $j = J^{-i} + 1,\ldots, J^{-i} + m$ from $G_0$. Then, we sample the cluster indicator 
    $\gamma_i$ from extant or candidate clusters, where the probability of cluster membership is proportional to
\begin{equation}
    \text{Pr}\left[\delta_i = j\mid\ldots\right] \propto \begin{cases}
        n_j^{-i}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right)\\ % \hspace{0.5cm}  % &\text{~for~}j \in \lbrace 1,\ldots,J^{-i}\rbrace\\
        \frac{\eta}{m}\mathcal{PG}\left(\bm{y}_i\mid\bm{\alpha}_j,\bm{\beta}_j\right). % \hspace{0.5cm} &\text{~for~}j \in \lbrace J^{-i} + 1,\ldots, J^{-i} + m\rbrace.
        \end{cases}
\end{equation}
Again, the top case is iterating over extant clusters, and now the bottom case is iterating 
    over new \emph{candidate} clusters.  If a candidate cluster is selected,
%{\bf you first have to say that you sample from this distribution. What is the ``candidate cluster''?}
    then $\gamma_i = J = J^{- i} + 1$, and the associated cluster parameters are saved.

@@

This model is completed with independent Gamma priors on $\xi_{\ell}$, $\tau_{\ell}$, $\zeta_{\ell}$, $\sigma_{\ell}$.  We also assume a Gamma prior on $\eta$, that is updated via the procedure outlined in \cite{escobar1995}.  We refer to this model as the \emph{projected gamma--gamma} (PG--G) model.  An advantage of the PG--G model is that, thanks to conjugacy, the rate parameters can easily be integrated out for inference on $\bm{\alpha}_j$.  Then, the full conditional for $\alpha_{j\ell}$ takes the form

@@

for $\ell = 2,\ldots, d$.  Updating $\beta_{j\ell}$ is done via a Gibbs step.  The hyper-parameters
$\xi_{\ell},\tau_{\ell},\zeta_{\ell},\sigma_{\ell}$ follow similar gamma-gamma update relationships.
We also explore a restricted form of this model, where $\beta_{\ell} = 1$ for all $\ell$.  Under this 
model, we use the full conditional in Equation~(\ref{eqn:alpha1update}) for all $\ell$, and omit 
inference on $\bm{\zeta},\bm{\sigma}$.  We refer to this model as the 
\emph{projected restricted gamma--gamma} (PRG--G) model.

The second form of centering distribution we explore is a multivariate log-normal distribution on the shape parameters $\bm{\alpha}_j$, with independent gamma $\beta_{j\ell}$ rate parameters.  
    \begin{equation}
        \begin{aligned}
        &\hspace{-0.5cm}G_0\left(\bm{\alpha}_j,\bm{\beta}_j\mid\bm{\mu},\bm{\Sigma},\zeta,\sigma\right) \\
        &=\mathcal{LN}\left(\bm{\alpha}_j\mid\bm{\mu},\bm{\Sigma}\right)\times\prod_{\ell = 2}^d\mathcal{G}\left(\beta_{j\ell}\mid\zeta_{\ell},\sigma_{\ell}\right).
        \end{aligned}
    \end{equation}
    This model is completed with a normal prior on $\bm{\mu}$, an inverse Wishart prior on
    $\bm{\Sigma}$, and Gamma priors on $\zeta_{\ell}$ and $\sigma_{\ell}$, and $\eta$.  
    This model is denoted as the \emph{projected gamma--log-normal} (PG--LN) model.  
    We also explore a restricted Gamma form of this model as above, where 
    $\beta_{\ell} = 1$ for all $\ell$.  This is denoted as the 
    \emph{projected restricted gamma--log-normal} (PRG--LN) model.  Updates for 
    $\bm{\alpha}$ can be accomplished using a joint Metropolis step, where 
    $\beta_{j\ell}$ for $\ell = 2,\ldots,d$ have been integrated out of the 
    log-density.  That is,
    \begin{equation*}
        \begin{aligned}
        &\hspace{-0.5cm}\pi(\bm{\alpha}_j\mid\bm{Y},\bm{r},\bm{\delta},\bm{\mu},\bm{\Sigma},\bm{\zeta},\bm{\sigma})\\
        &\propto \exp\left\lbrace-\frac{1}{2}(\log\bm{\alpha}_j - \mu)^T\bm{\Sigma}^{-1}(\log\bm{\alpha}_j - \mu)\right\rbrace \\
        &\hspace{0.5cm}\times\frac{1}{\prod_{\ell = 1}^d\alpha_{j\ell}}\times \frac{\left(\prod_{i:\gamma_i = j}r_iy_{i1}\right)^{\alpha_{j1} - 1}}{\prod_{\ell = 1}^d\Gamma^{n_j}(\alpha_{j\ell})}\\
        &\hspace{0.5cm}\times \prod_{\ell = 2}^d\frac{\Gamma\left(n_j\alpha_{j\ell} + \zeta_{\ell}\right)}{\left(\sum_{i:\gamma_i = j}r_iy_{i\ell} + \sigma_{\ell}\right)^{n_j\alpha_{j\ell} + \zeta_{\ell}}}
        \end{aligned}
    \end{equation*}
    The inferential forms for $\beta_{j\ell}$ and its priors are the same as for PG--G.  The 
  normal prior for $\mu$ is conjugate for the log-normal $\bm{\alpha}_j$, and can be sampled
  via a Gibbs step.  Finally, the inverse Wishart prior for $\Sigma$ is again conjugate to
  the log-normal $\bm{\alpha}_j$, implying that it can also be sampled via a Gibbs step.
